### 2015-07-03 Body/Conclusions/Conclusions.Rnw

\km{The study on traditional and simulation-based statistical inference curricula took an ambitious and statistically rigorous approach to comparing learning outcomes through a designed experiment. The randomization of students to curricula helped to isolate the curricular effect by creating homogenous cohorts of students which received each curriculum. The student learning outcomes, measured using the ARTIST scaled questions sets for confidence intervals and hypothesis tests, were analyzed using a bivariate MANCOVA model which controls for pre-treatment factors, including scores from a midterm and lab. The model found no significant curriculum effect for learning outcomes related to hypothesis tests; despite the added complexity in the simulation-based curriculum. The model also indicates a statistically significant 7\% improvement on the ARTIST scale for the simulation-based curriculum over the traditional curriculum for learning outcomes related to confidence intervals, while accounting for pre-treatment covariates. However, the validity of these results is highly questionable because the model assumption of independence between students is likely untrue. The simulation study demonstrated that the Type I error rates in tests for curricular effects inflate dramatically under minor violations that have lecture or lab section based variance structure. Therefore, caution must be taken in interpreting the results of this study which are suggestive, but not conclusive, of a simulation-based curriculum benefit.}

>>>>

\km{The study on traditional and simulation-based statistical inference curricula took an ambitious and statistically rigorous approach to comparing learning outcomes through a designed experiment. The randomization of students to curricula helped to isolate the curricular effect by creating homogeneous cohorts of students which received each curriculum. The student learning outcomes, measured using the ARTIST scaled questions sets for confidence intervals and hypothesis tests, were analyzed using a bivariate MANCOVA model which controls for pre-treatment factors, including scores from a midterm and lab. The model found no significant curriculum effect for learning outcomes related to hypothesis tests; despite the added complexity in the simulation-based curriculum. The model also indicates a statistically significant 7\% improvement on the ARTIST scale for the simulation-based curriculum over the traditional curriculum for learning outcomes related to confidence intervals, while accounting for pre-treatment covariates. However, the validity of these results is highly questionable because the model assumption of independence between students is likely untrue. The simulation study demonstrated that the Type I error rates in tests for curricular effects inflate dramatically under minor violations that have lecture or lab section based variance structure. Therefore, caution must be taken in interpreting the results of this study which are suggestive, but not conclusive, of a simulation-based curriculum benefit.}
